Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
remove real-time., real-time is not important here and might confuse the reader
explanation how important real-time processing is for this project is required #15

Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.

@@

\subsection{Standard CI/CD DevOps}
The development and deployment of KUB builds on top of the Feel++ CI/CD framework. It employs GitHub Actions and Docker: GitHub Actions automate real-time workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
On the other hand, Docker provides a containerized environment that encapsulates Feel++ and its dependencies, ensuring consistent operations across diverse computing environments.
These Docker images, customized for various system requirements, are maintained on the GitHub Container Registry (ghcr.io) to accommodate multiple deployment scenarios.

>>>>

Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.

@@

\subsection{Standard CI/CD DevOps}
The development and deployment of KUB builds on top of the Feel++ CI/CD framework. It employs GitHub Actions and Docker: GitHub Actions automate workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
On the other hand, Docker provides a containerized environment that encapsulates Feel++ and its dependencies, ensuring consistent operations across diverse computing environments.
These Docker images, customized for various system requirements, are maintained on the GitHub Container Registry (ghcr.io) to accommodate multiple deployment scenarios.
